~\Large Increased sexual dimorphism does not evolve in a fossil stickleback following ecological release from fish piscivores

### 2024-11-01 manuscript/paper.tex
knit productions

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2034}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0847}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.7119}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Trait Name
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Trait Code
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Trait Description
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Standard Length & \texttt{stl} & Distance from anterior tip of
premaxilla to posterior end of last vertebra (i.e., the llhypural
plate) \\
Dorsal Spine Count & \texttt{mds} & Number of dorsal spines \\
Dorsal Fin Ray Count & \texttt{mdf} & Number of bones in the dorsal fin
posterior to the third dorsal spine (i.e., soft dorsal fin rays) \\
Anal Fin Ray Count & \texttt{maf} & Number of bones in the anal fin
posterior to the anal spine (i.e., soft anal fin rays) \\
Abdominal Vertebra Count & \texttt{mav} & Number of vertebrae anterior
to the first vertebra contacting an anal fin pterygiophore (Aguirre et
al.~2014) \\
Caudal Vertebra Count & \texttt{mcv} & Vertebrae including and posterior
to the first that contacts an anal fin pterygiophore (Aguirre et
al.~2014) \\
Pterygiophore Count & \texttt{mpt} & Number of pterygiophores anterior
to but excluding the pterygiophore under the third dorsal spine \\
Pelvic Spine Length & \texttt{lps.sc} & Length from the base of one
pelvic spine at its pelvic girdle articulation to its distal tip \\
Ectocoracoid Length & \texttt{ect.sc} & Length from the anterior to
posterior tips of the shoulder girdle base \\
Pelvic Girdle Length & \texttt{tpg.sc} & Length from the anterior to
posterior tips along midline. If vestigial, the sum of longest axis
along vestiges \\
Cleithrum Length & \texttt{cle.sc} & Length from dorsal tip to ventral
tip on the anterior margin of the shoulder girdle \\
Premaxilla Length & \texttt{pmx.sc} & Length from the anterior tip of
the premaxilla to the distal tip of its ascending process \\
Dorsal Spine Length & \texttt{Ds\#.sc\ \#=1/2/3} & Length from the
dorsal spine base at the pterygiophore to its distal tip \\
Pterygiophore Length & \texttt{lpt.sc} & Distance from anterior to
posterior edges of the pterygiophore immediately before ds3 (when
present) \\
\end{longtable}

>>>>

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.2034}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.0847}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 4\tabcolsep) * \real{0.7119}}@{}}
\toprule()
\begin{minipage}[b]{\linewidth}\raggedright
Trait Name
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Trait Code
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Trait Description
\end{minipage} \\
\midrule()
\endhead
Standard Length & \texttt{stl} & Distance from anterior tip of
premaxilla to posterior end of last vertebra (i.e., the llhypural
plate) \\
Dorsal Spine Count & \texttt{mds} & Number of dorsal spines \\
Dorsal Fin Ray Count & \texttt{mdf} & Number of bones in the dorsal fin
posterior to the third dorsal spine (i.e., soft dorsal fin rays) \\
Anal Fin Ray Count & \texttt{maf} & Number of bones in the anal fin
posterior to the anal spine (i.e., soft anal fin rays) \\
Abdominal Vertebra Count & \texttt{mav} & Number of vertebrae anterior
to the first vertebra contacting an anal fin pterygiophore (Aguirre et
al.~2014) \\
Caudal Vertebra Count & \texttt{mcv} & Vertebrae including and posterior
to the first that contacts an anal fin pterygiophore (Aguirre et
al.~2014) \\
Pterygiophore Count & \texttt{mpt} & Number of pterygiophores anterior
to but excluding the pterygiophore under the third dorsal spine \\
Pelvic Spine Length & \texttt{lps.sc} & Length from the base of one
pelvic spine at its pelvic girdle articulation to its distal tip \\
Ectocoracoid Length & \texttt{ect.sc} & Length from the anterior to
posterior tips of the shoulder girdle base \\
Pelvic Girdle Length & \texttt{tpg.sc} & Length from the anterior to
posterior tips along midline. If vestigial, the sum of longest axis
along vestiges \\
Cleithrum Length & \texttt{cle.sc} & Length from dorsal tip to ventral
tip on the anterior margin of the shoulder girdle \\
Premaxilla Length & \texttt{pmx.sc} & Length from the anterior tip of
the premaxilla to the distal tip of its ascending process \\
Dorsal Spine Length & \texttt{Ds\#.sc\ \#=1/2/3} & Length from the
dorsal spine base at the pterygiophore to its distal tip \\
Pterygiophore Length & \texttt{lpt.sc} & Distance from anterior to
posterior edges of the pterygiophore immediately before ds3 (when
present) \\
\bottomrule()
\end{longtable}
